Manuscript

### 2018-12-13 manuscript.Rmd

# ggsave("./plots/manuscript/crispr_data_signif_g2p_lineage_plot.png", crispr_data_signif_g2p_lineage_plot, width = 15, height = 18, units = "in")
```

@@

ccle_signif_g2p_grid <- readRDS("./data_munging/rds/ccle_signif_g2p_grid.rds")
knitr::kable(ccle_signif_g2p_grid[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

ctrp_signif_g2p_grid <- readRDS("./data_munging/rds/ctrp_signif_g2p_grid.rds")
knitr::kable(ctrp_signif_g2p_grid[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

gdsc_signif_g2p_grid <- readRDS("./data_munging/rds/gdsc_signif_g2p_grid.rds")
knitr::kable(gdsc_signif_g2p_grid[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

ctrp_summ_res_mut_plot <- ggplot(data = subset(ctrp_res_mut, p < 0.05)) +
  facet_grid(Dataset ~ Metric) +
  # scale_y_continuous(breaks = seq(0, 30, by = 5), labels = seq(0, 30, by = 5)) +
  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
  geom_text_repel(mapping = aes(y = p_log10, x = corr, label = Drug_Gene, color = Metric), force = 10, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 1) +
  theme(legend.position = "none", panel.grid.major.x = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(5.5, 1.5, 5.5, 5.5), "pt"), strip.background.y = element_blank(), strip.text.y = element_blank()) +
  scale_color_manual(values = c("Mutation Status" = "darkorchid4")) +
  labs(y = "-log10(p-value)")

ctrp_summ_res_pearson_plot <- ggplot(data = subset(ctrp_pearson_res_filt, p < 0.05)) +
  facet_grid(Dataset ~ Metric) +
  scale_y_continuous(breaks = seq(0, 30, by = 5), labels = seq(0, 30, by = 5)) +
  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
  geom_text_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Drug_Gene), force = 10, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
  theme(legend.position = "none", plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
  labs(x = "Pearson correlation coefficient (r)")

@@

gdsc_summ_res_mut_plot <- ggplot(data = subset(gdsc_res_mut, p < 0.05)) +
  facet_grid(Dataset ~ Metric) +
  # scale_y_continuous(breaks = seq(0, 30, by = 5), labels = seq(0, 30, by = 5)) +
  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
  geom_text_repel(mapping = aes(y = p_log10, x = corr, label = Drug_Gene, color = Metric), box.padding = 0.75, force = 15, size = 2.5, segment.size = 0.2, segment.colour = "grey50") +
  theme(legend.position = "none", panel.grid.major.x = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(5.5, 1.5, 5.5, 5.5), "pt"), strip.background.y = element_blank(), strip.text.y = element_blank()) +
  scale_color_manual(values = c("Mutation Status" = "darkorchid4")) +
  labs(y = "-log10(p-value)")

gdsc_summ_res_pearson_plot <- ggplot(data = subset(gdsc_pearson_res_filt, p < 0.05)) +
  facet_grid(Dataset ~ Metric) +
  # scale_y_continuous(breaks = seq(0, 30, by = 5), labels = seq(0, 30, by = 5)) +
  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
  geom_text_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Drug_Gene), force = 10, nudge_y = 2.5, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
  theme(legend.position = "none", plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
  labs(x = "Pearson correlation coefficient (r)", y = "-log10(p-value)")

@@

ItemsList <- venn(dgl_overlap_test_list, show.plot=TRUE)
```

@@

g2p_dgl_summ <- merge(merge(ccle_dgl_summ, ctrp_dgl_summ, by = c("Drug", "Gene", "Lineage"), all = TRUE), gdsc_dgl_summ, by = c("Drug", "Gene", "Lineage"), all = TRUE)
```

>>>>

# write.table(crispr_data_signif_g2p_lineage, file = "~/Desktop/crispr_data_signif_g2p_lineage_20181213.tsv", quote = FALSE, sep = "\t")
# ggsave("./plots/manuscript/crispr_data_signif_g2p_lineage_plot.png", crispr_data_signif_g2p_lineage_plot, width = 15, height = 18, units = "in")
```

@@

ccle_signif_g2p_grid <- readRDS("./data_munging/rds/ccle_signif_g2p_grid.rds")
knitr::kable(ccle_signif_g2p_grid[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

ctrp_signif_g2p_grid <- readRDS("./data_munging/rds/ctrp_signif_g2p_grid.rds")
knitr::kable(ctrp_signif_g2p_grid[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

gdsc_signif_g2p_grid <- readRDS("./data_munging/rds/gdsc_signif_g2p_grid.rds")
knitr::kable(gdsc_signif_g2p_grid[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

ctrp_summ_res_mut_plot <- ggplot(data = subset(ctrp_res_mut, p < 0.05)) +
  facet_grid(Dataset ~ Metric) +
  scale_y_continuous(breaks = seq(0, 10, by = 1), labels = seq(0, 10, by = 1)) +
  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
  geom_text_repel(mapping = aes(y = p_log10, x = corr, label = Drug_Gene, color = Metric), force = 50, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 1.5) +
  theme(legend.position = "none", panel.grid.major.x = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(5.5, 1.5, 5.5, 5.5), "pt"), strip.background.y = element_blank(), strip.text.y = element_blank()) +
  scale_color_manual(values = c("Mutation Status" = "darkorchid4")) +
  labs(y = "-log10(p-value)")

ctrp_summ_res_pearson_plot <- ggplot(data = subset(ctrp_pearson_res_filt, p < 0.05)) +
  facet_grid(Dataset ~ Metric) +
  scale_y_continuous(breaks = seq(0, 30, by = 5), labels = seq(0, 30, by = 5)) +
  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
  geom_text_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Drug_Gene), force = 10, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
  theme(legend.position = "none", plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt"), axis.title.y = element_blank()) +
  labs(x = "Pearson correlation coefficient (r)")

@@

gdsc_summ_res_mut_plot <- ggplot(data = subset(gdsc_res_mut, p < 0.05)) +
  facet_grid(Dataset ~ Metric) +
  scale_y_continuous(breaks = seq(0, 16, by = 1), labels = seq(0, 16, by = 1)) +
  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
  geom_text_repel(mapping = aes(y = p_log10, x = corr, label = Drug_Gene, color = Metric), box.padding = 1, nudge_y = 0.75, force = 20, size = 2.5, segment.size = 0.2, segment.colour = "grey50") +
  theme(legend.position = "none", panel.grid.major.x = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(5.5, 1.5, 5.5, 5.5), "pt"), strip.background.y = element_blank(), strip.text.y = element_blank()) +
  scale_color_manual(values = c("Mutation Status" = "darkorchid4")) +
  labs(y = "-log10(p-value)")

gdsc_summ_res_pearson_plot <- ggplot(data = subset(gdsc_pearson_res_filt, p < 0.05)) +
  facet_grid(Dataset ~ Metric) +
  scale_y_continuous(breaks = seq(0, 100, by = 10), labels = seq(0, 100, by = 10)) +
  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
  geom_text_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Drug_Gene), force = 10, nudge_y = 2.5, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
  theme(legend.position = "none", plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt"), axis.title.y = element_blank()) +
  labs(x = "Pearson correlation coefficient (r)", y = "-log10(p-value)")

@@

ItemsList <- venn(dgl_overlap_test_list, show.plot = TRUE)
ItemsList
```

@@

g2p_dgl_sig_summ <- merge(merge(ccle_dgl_summ, ctrp_dgl_summ, by = c("Drug", "Gene", "Lineage"), all = TRUE), gdsc_dgl_summ, by = c("Drug", "Gene", "Lineage"), all = TRUE)
```
